Summer 2025 ToDo

### 2025-11-13 Relations/Paper/Introduction.tex

\section{Introduction}
\label{sec:Introduction}

@@

We present a formalization of the basic Abstract Rewriting Systems (ARS) theory as presented in Term Rewriting Systems [TeReSe]
 \cite{Terese}, using the Agda proof assistant.
This work is part of a larger effort to develop a library of formalized programming language theory (PL)
at Appalachian State University.
Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
while ARS encompass the basic facts about rewriting relations in general,
establishing these facts is part of the necessary infrastructure required to
pursue the broader project.  The present contribution can therefore be seen as
``bootstrapping'' Appstate's new formalized PL repository.

@@

Recall that a relation is strongly normalizing iff its converse is well-founded. \cite[Def.1.1.13]{Terese}.
Since normalization is a central concept in ARS theory,
we pay special attention to the concept of well-foundedness.
The standard constructive definition does not even allow one to show that SN implies WN,
as we discuss in Section \ref{sec:Well-foundedness} and formalize in \texttt{WFCounters.agda}.
We therefore looked at a number of variations of this notion in the constructive context,
their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.

>>>>

\section{Introduction}

\newcommand{\inreview}[1]{[\textsc{university name}]}
% \newcommand{\inreview}[1]{\sout{\phantom{#1}}}
% \newcommand{\inreview}[1]{#1}

\label{sec:Introduction}

@@

We present a formalization of the basic Abstract Rewriting Systems (ARS) theory as presented in Term Rewriting Systems [TeReSe]
 \cite{Terese}, using the Agda proof assistant.
This work is part of a larger effort to develop a library of formalized programming language theory (PL)
at \inreview{Appalachian State} University.
Since Term Rewriting Systems (TRS) play a foundational role in programming languages,
while ARS encompass the basic facts about rewriting relations in general,
establishing these facts is part of the necessary infrastructure required to
pursue the broader project.  The present contribution can therefore be seen as
``bootstrapping'' \inreview{Appalachian State}'s new formalized PL repository.

@@

Recall that a relation is strongly normalizing iff its converse is well-founded. \cite[Def.1.1.13]{Terese}.
Since normalization is a central concept in ARS theory,
we pay special attention to the concept of well-foundedness.
The standard constructive definition does not even allow one to show that SN implies WN,
as we discuss at the end of Section \ref{sec:Well-foundedness} and formalize in \texttt{ARS/Examples.agda}. We therefore looked at a number of variations of this notion in the constructive context,
their classical counterparts all being logically equivalent. %This gave rise to a rich set of concepts, see Figure \ref{f:wf}.
